Exploring 2 variables: Scatterplots, Correlation, Conditional Means.
======================================================== 

***

### Scatterplots and Perceived Audience Size
Notes: People actually have more audience than they think

***

### Scatterplots  
Notes:  
+ we only looked at distributions of single variables e.g. friend_count; atmost their subsets split across different factors e.g. gender.
+ we move onto two continous variables at the same time.
+ qplot auto-chooses a scatter plot when fed with two continous variables to the x,y params
+ try with x=age, y=friend_count --> pf 

```{r Scatterplots}
library(ggplot2)
getwd()
pf = read.csv('pseudo_facebook.tsv', sep = '\t')
# qplot(age, friend_count, data=pf)  --> alternative
ggplot(aes(x = age, y = friend_count), data = pf) +
  geom_point()
```

***

#### What are some things that you notice right away?
Response:
+ generally friend count reduces with increasing age.
+ some older users are quite popular as well -> probably younger people who lied about their age 

***

### ggplot Syntax
Notes:
+ helps specify more complicated plots
+ we have an aesthetic wrapper and need to specify the type of plot we want (point - for a scatter plot)

```{r ggplot Syntax}
## ggplot vs qplot
# qplot(age, friend_count, data=pf)  --> alternative
ggplot(aes(x = age, y = friend_count), data = pf) +    ## we have an aesthetic wrapper and need
  geom_point() 

## we need to figure out the upper and lower age limits
summary(pf$age)
```
```{r ggplot syntax - continued}
ggplot(aes(x = age, y = friend_count), data = pf) +    ## we have an aesthetic wrapper and need
  geom_point() + ## use the + operator to add layers to our plot
  xlim(13, 90)
```
***

### Overplotting
Notes:
+ points over each other
+ makes it hard to tell how many points are in a region
+ solution: set transparency of points using the "alpha" parameter in geom_point()

```{r Overplotting}
ggplot(aes(x = age, y = friend_count), data = pf) +    ## we have an aesthetic wrapper and need
  geom_point( alpha = 1/20) + ## use the + operator to add layers to our plot --> meaning 20 points to be the equivalent of one black dot
  xlim(13, 90)
```
## Replacing geom_point with geom_jitter to add some jitter
```{r geom_jitter}
ggplot(aes(x=age, y=friend_count), data = pf) + 
  geom_jitter(alpha = 1/20) + 
  xlim(13, 90)

```


#### What do you notice in the plot?
Response:
+ the bulk of our data mainly lies below the 1000 threshold for friend count
+ young users dont have as many friends as it appeared before.

***

### Coord_trans()
Notes:
+ It is easier to see friend_count conditional on age with sqrt function

```{r Coord_trans()}
ggplot(aes(x = age, y = ifelse(is.na(friend_count), 10, friend_count)), data = pf) + 
  geom_point(alpha = 1/20 ) + 
  xlim(13, 90) + 
  coord_trans(y = 'sqrt')
  
```

#### Look up the documentation for coord_trans() and add a layer to the plot that transforms friend_count using the square root function. Create your plot!

```{r}
## Jitter can add +ve or -ve noise - directly using coord_trans( .. 'sqrt') calculates sqrt of negative values which throws exceptions
ggplot(aes(x = age, y =  friend_count), data = pf) + 
  geom_point(alpha = 1/20, position = position_jitter( h = 0) ) + # prevents the Error in if (zero_range(range)) { : missing value where TRUE/FALSE needed
  xlim(13, 90) + 
  coord_trans(y = 'sqrt')
```

#### What do you notice?
+ It is easier to see the the relation between friendship count and age. 
+ also friend ship count is not as high as it was.
***

### Alpha and Jitter
Notes:
+ generally younger people initiate more friendships than older people

```{r Alpha and Jitter}
ggplot(aes(x = age, y =  friendships_initiated), data = pf) + 
  geom_point()
```
### Now adding some alpha jitter
*** 
+ we notice that the number of friendships initiated reduces significantly
+ also the trend becomes much clearer i.e. that younger people initiate more frienships
```{r Alpha and Jitter 2}
ggplot(aes(x = age, y =  friendships_initiated), data = pf) + 
  geom_point(alpha = 1/20, position = position_jitter( h = 0)) +
  xlim(13, 90) + 
  coord_trans(y = 'sqrt')
```
```{r Alpha and Jitter 3}
## it becomes even much better with 150th set as the alpha value
ggplot(aes(x = age, y =  friendships_initiated), data = pf) + 
  geom_point(alpha = 1/50, position = position_jitter( h = 0))+  ### take out these layers for a clearer picture
  xlim(13, 90) + 
  coord_trans(y = 'sqrt')
```
***

### Overplotting and Domain Knowledge
Notes:
+ using percentages gives a much clearer picture of the situation

***

### Conditional Means
Notes:
+ We may sometimes need to compare the means and/or medians of variables 
+ or simply compare the two using other ways than plotting every simple point  e.g. average(friend_count Vs age)
```{r Conditional Means}
# we need to make use of the dplyr package
library(dplyr)
# 1. group data by age
age_groups = group_by(pf, age)
# 2. create the variables you wish to create from the summarised new data_frame
pf.fc_by_age = summarise(age_groups,    
          friend_count_mean = mean(friend_count), 
          friend_count_median = median(friend_count), 
          n = n()) # n() can only be used in the summarise function. --> returns the number of people in each group
# finally add the entire friend_count_by_age saga to the pf dataset

pf.fc_by_age = arrange(pf.fc_by_age, age) ## it can be arranged by age

## now to review the first rows of the new data frame using the head function
head(pf.fc_by_age)
```
### Alternate way to apply functions onto our pf dataset
```{r}
# library(dplyr)
## Make use of the %.% : allows us to chain functions onto the desired dataset
pf.fc_by_age = pf %>% 
  group_by(age) %>% # first group it by age, then ...
  summarise(friend_count_mean = mean(friend_count),  ## summarise the groups using mean, median then ...
            friend_count_median = median(friend_count),
            n = n()) %>% #  retrieve the number of elements(people) in each group then finally ...
  arrange(age) # arrange the results by age 

## it can be saved to a variable (pf.fc_by_age)
## check the results of the new code to see if it matches --> and we get the exact same results. U can print as many rows as you wish by specifying the numberin the head function.
head(pf.fc_by_age, 15)

```

Create your plot!

```{r Conditional Means Plot}
ggplot(aes(age, pf.fc_by_age$friend_count_mean), data = pf.fc_by_age) + 
  geom_line() 
```

***

### Overlaying Summaries with Raw Data
Notes:
we can overlay summary information over the original data easily using ggplot

```{r Overlaying Summaries with Raw Data}
ggplot(aes(x = age, y =  friendships_initiated), data = pf) + 
  geom_point(alpha = 0.05, position = position_jitter( h = 0), 
             color = 'orange')+  ### take out these layers for a clearer picture
  xlim(13, 90) + 
  coord_trans(y = 'sqrt') + 
  geom_line(stat = 'summary', fun.y = mean ) +  # apply the mean function to the y values and overlay it on the original plot
  geom_line(stat = 'summary', fun.y = quantile, fun.args=list(probs=0.1),  # 10% mark
            linetype = 2, color = 'blue') +  
   geom_line(stat = 'summary', fun.y = quantile, fun.args=list(probs=0.5), # 50% mark 
             color = 'blue') +
  geom_line(stat = 'summary', fun.y = quantile, fun.args=list(probs=0.9),  # 90% mark
            linetype = 2, color = 'blue')
```

#### What are some of your observations of the plot?
Response:

***
```{r coord_cartesian}
ggplot(aes(x = age, y =  friendships_initiated), data = pf) + 
  geom_point(alpha = 0.05, position = position_jitter( h = 0), 
             color = 'orange')+  ### take out these layers for a clearer picture
  coord_cartesian(xlim = c(13, 70), ylim = c(0,1000)) + 
  geom_line(stat = 'summary', fun.y = mean ) +  # apply the mean function to the y values and overlay it on the original plot
  geom_line(stat = 'summary', fun.y = quantile, fun.args=list(probs=0.1),  # 10% mark
            linetype = 2, color = 'blue') +  
   geom_line(stat = 'summary', fun.y = quantile, fun.args=list(probs=0.5), # 50% mark 
             color = 'blue') +
  geom_line(stat = 'summary', fun.y = quantile, fun.args=list(probs=0.9),  # 90% mark
            linetype = 2, color = 'blue')

```

### Moira: Histogram Summary and Scatterplot
See the Instructor Notes of this video to download Moira's paper on perceived audience size and to see the final plot.

Notes:
+ Histograms sometimes bring out the big picture much more clearer
+ using the facebook audience case study, there are more underestimations than over estimations

***

### Correlation
Notes:
+ Using the cor.test function we can find the correlation between paired samples
+ Some times it's much easier and better to use a single value compairing the relation of two variables

```{r Correlation}
# correlation between age and friend count
cor.test(pf$age, pf$friend_count, 
         conf.level = 0.95, method = 'pearson')

## Alternatively
# with(pf, cor.test(age, friend_count, method = 'pearson'))
```

Look up the documentation for the cor.test function.

What's the correlation between age and friend count? Round to three decimal places.
Response:
+ -0.02740737 implies there's no meaningful relationship between the two of them i.e for cor = 0.3 orless
***

### Correlation on Subsets
Notes: 
+ we get a negative value showing that as age increases, their number of friends decreases.
+ it should be noted, however, that one does not cause the other.

```{r Correlation on Subsets}
with(  subset(pf, age<=70, select = c(age, friend_count)), cor.test(age, friend_count))
```

***

### Correlation Methods
Notes: methods include: pearson, spearman, kendall

***

## Create Scatterplots
Notes: likes_received(y) vs www_likes_received(x)

```{r}
ggplot(aes(www_likes_received, likes_received), data = pf) + 
  geom_point()
```

***

### Strong Correlations
Notes: 
+ we have got quite the outliers
+ use the 95th percentiles to get a good idea of good upper bounds for axes

```{r Strong Correlations}
ggplot(aes(www_likes_received, likes_received), data = pf) + 
  geom_point() + 
  xlim(0, quantile(pf$www_likes_received, 0.95)) + # for the upper bound on the x axis
  ylim(0, quantile(pf$likes_received, 0.95)) +     # for the upper bound on the ys axis
  geom_smooth(method = 'lm', color = 'blue')        # get the correlation using geom_smooth function with a linear model
```

What's the correlation betwen the two variables? Include the top 5% of values for the variable in the calculation and round to 3 decimal places.

```{r Correlation Calcuation}
with(pf, cor.test(www_likes_received, likes_received))
```

Response:
+ There is a very strong positive correlation

***

### Moira on Correlation
Notes:
+ correlation helps us find out which variables are related
***

### More Caution with Correlation
Notes:
+ correlations can be deceptive
+ plotting data is generally the sure way
```{r More Caution With Correlation}
#install.packages(alr3)
library(alr3)
```

Create your plot!

```{r Temp vs Month}
data("Mitchell")
ggplot(aes( Month, Temp ), data = Mitchell) + 
  geom_point()
```

***

### Noisy Scatterplots
a. Take a guess for the correlation coefficient for the scatterplot. 
   Their correlation should be 0

b. What is the actual correlation of the two variables?
(Round to the thousandths place)

```{r Noisy Scatterplots}
cor.test(Mitchell$Month, Mitchell$Temp)

```

***

### Making Sense of Data
Notes:
+ Need to break up the months( x-axis ) into 12 bits so that it corresponds to a year

```{r Making Sense of Data}
ggplot(aes( Month, Temp ), data = Mitchell) + 
  geom_point()+
  scale_x_continuous(breaks = seq(0, 203, 12)) 
```

***

### A New Perspective

What do you notice?
Response:
```{r}
ggplot(aes(x=(Month%%12),y=Temp), data=Mitchell)+
  geom_point()
```


Watch the solution video and check out the Instructor Notes!
Notes:
+ after stretching it out, we notice that the graph forms a sinusoidal curve
***

### Understanding Noise: Age to Age Months
Notes:
+ ages are noisy
+ might make more sense to work with age in months instead of years
```{r Understanding Noise: Age to Age Months}

ggplot(aes(age, friend_count_mean), data = pf.fc_by_age) + 
  geom_line()

```

***

### Age with Months Means

```{r Age with Months Means}
## creating age_with_months variable
pf$age_with_months = pf$age + (1 - pf$dob_month / 12 )

```

Programming Assignment
```{r Programming Assignment}
pf$age_with_months = pf$age + (1 - pf$dob_month / 12 )
# 1. group data by age
age_month_groups = group_by(pf, age_with_months)
# 2. create the variables you wish to create from the summarised new data_frame
pf.fc_by_age_months = summarise(age_month_groups,    
          friend_count_mean = mean(friend_count), 
          friend_count_median = median(friend_count), 
          n = n()) # n() can only be used in the summarise function. --> returns the number of people in each group
# finally add the entire friend_count_by_age saga to the pf dataset

pf.fc_by_age_months = arrange(pf.fc_by_age_months, age_with_months) ## it can be arranged by age

## now to review the first rows of the new data frame using the head function
head(pf.fc_by_age_months)
```

***

### Noise in Conditional Means

```{r Noise in Conditional Means}
ggplot(aes( age_with_months,  friend_count_mean), data = subset(pf.fc_by_age_months, age_with_months < 71)) +
  geom_line()

```

***

### Smoothing Conditional Means
Notes:

```{r Smoothing Conditional Means}

p1 = ggplot(aes(age, friend_count_mean), data = subset(pf.fc_by_age, age < 71)) + 
  geom_line() 

p2 = ggplot(aes(age_with_months, friend_count_mean), data = subset(pf.fc_by_age_months, age_with_months < 71)) + 
  geom_line()

p3 = ggplot(aes(round(age / 5) * 5, friend_count), data = subset(pf, age < 71)) + 
  geom_line( stat = 'summary', fun.y = mean)

library(gridExtra)
grid.arrange(p2, p1, p3, ncol = 1)

```

```{r after smoothing the graphs}
p1 = ggplot(aes(age, friend_count_mean), data = subset(pf.fc_by_age, age < 71)) + 
  geom_line() +
  geom_smooth()


p2 = ggplot(aes(age_with_months, friend_count_mean), data = subset(pf.fc_by_age_months, age_with_months < 71)) + 
  geom_line() +
  geom_smooth()

p3 = ggplot(aes(round(age / 5) * 5, friend_count), data = subset(pf, age < 71)) + 
  geom_line( stat = 'summary', fun.y = mean)

grid.arrange(p2, p1, p3, ncol = 1)
```


***

### Which Plot to Choose?
Notes:
+ some continuities are missed
+ hence, sometimes the smoothener is subjected to systematic errors
***

### Analyzing Two Variables
Reflection:
+ you dont really have to choose a type of plot to use
+ conditional means, smoothening
+ correlation
+ scatter plots
***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

