---
title: "Problem Set 2 Variable Exploration"
author: "Alex Gunagwera"
date: "24 Mart 2018"
output: html_document
---

ProblemSet: Explore Two Variables
========================================================

### Welcome
Notes: Let's breeze through this 

***
### ggpairs Function
Notes:

```{r ggpairs Function}
# install these if necessary
# install.packages('GGally')
# install.packages('scales')
# install.packages('memisc')
# install.packages('lattice')
# install.packages('MASS')
# install.packages('car')
# install.packages('reshape')
# install.packages('plyr')

# load the ggplot graphics package and the others
library(ggplot2)
library(GGally)
library(scales)
library(memisc)
```



### Scatterplot Review

```{r Scatterplot Review}
db = read.csv('diamondsbig.csv')
d = diamonds
summary(db)
library(ggplot2)

# Now the scatter plot
ggplot(aes(x, price), data = db) +
  geom_point()

```

+ Ignoring the outliers, price increases exponentially with x
+ the scatter plot is definitely overplotted
***

### Correlations
```{r correlation between price and y}
structure(rapply(cor.test(d$x, d$price),function(x) if(is.numeric(x)) round(x,2) else x,how="replace"),
  class="htest")
```
```{r correlation between price and y - 2}
structure(rapply(cor.test(d$y, d$price),function(x) if(is.numeric(x)) round(x,2) else x,how="replace"),
  class="htest")
```
```{r correlation between price and z}
structure(rapply(cor.test(d$z, d$price),function(x) if(is.numeric(x)) round(x,2) else x,how="replace"),
  class="htest")
```
### Simple Scatter of price vs depth
```{r Simple Scatter of price vs depth }
ggplot(aes(round(depth / 2)*2, price), data = d) +
  geom_point(alpha = 1/100)
```
### Price Vs Depth correlation
```{r depth vs price}
structure(rapply(cor.test(d$depth, d$price),function(x) if(is.numeric(x)) round(x,2) else x,how="replace"),
  class="htest")

```

### Price and Carat Relationship
Response:
Omit the top 1% of each. Draw a scatter plot
```{r omit the top 1 percent }
ggplot(aes(carat, price), data = diamonds) + 
  geom_point() + 
  xlim(0, quantile(d$carat, 0.99)) + # for the upper bound on the x axis
  ylim(0, quantile(d$price, 0.99)) 

```

```{r volume of a diamond }
## create volume into diamond
d$volume = d$x * d$y * d$z

# Now create a scatter plot of price Vs volume
ggplot(aes(volume, price), data = d) +
  geom_point()
```
### Correlation of price vs Volume (ignore 0 or >= 800)
```{r Price Vs Volume correlation | Correlations on subsets}
# 1. first create a subset with desired conditions
subdiamonds = subset(d, (d$volume != 0) & (d$volume < 800)) 

# 2. calculate desired correlation
cor.test(subdiamonds$price, subdiamonds$volume)             

```
### Adjustments on the price vs volume scatter plot
```{r Adjustments - price vs. volume }
# 1. first create a subset with desired conditions
subdiamonds = subset(d, (d$volume != 0) & (d$volume < 800))

ggplot(aes(volume, price), data = subdiamonds) +
  geom_point(alpha = 1/50) + 
  geom_smooth(method = 'lm')
```

***

### Mean price by clarity
```{r Mean Price by clarity}
suppressMessages(library(ggplot2))
suppressMessages(library(dplyr))
diamondsByClarity = subdiamonds %>%
  group_by(clarity) %>%
  summarise(
    mean_price   = mean(price),
    median_price = median(price),
    min_price    = min(price),
    max_price    = max(price),
    n            = n()  
  )

suppressMessages(summary(diamondsByClarity, 6))
```

### Bar Charts of Mean price
#### In this task, we are required to write additional code to create two bar plots
#### on one output image using the grid.arrange() function from the package
#### gridExtra.
```{r mean price by clarity bar charts}

diamonds_by_clarity = group_by(diamonds, clarity)
diamonds_mp_by_clarity = summarise(diamonds_by_clarity, mean_price = mean(price))

diamonds_by_color = group_by(diamonds, color)
diamonds_mp_by_color = summarise(diamonds_by_color, mean_price = mean(price))

# 1. make first barchart
b1 = ggplot(aes(clarity, mean_price), data = diamonds_mp_by_clarity) + 
geom_bar(stat = 'identity')

# 2. make second barchart
b2 = ggplot(aes(color, mean_price), data = diamonds_mp_by_color) + 
geom_bar(stat = 'identity')

library(gridExtra)
grid.arrange(b1, b2, ncol = 1)
```

### Mean price across cut
```{r mean price by cut bar charts}

diamonds_by_clarity = group_by(diamonds, clarity)
diamonds_mp_by_clarity = summarise(diamonds_by_clarity, mean_price = mean(price))

diamonds_by_color = group_by(diamonds, color)
diamonds_mp_by_color = summarise(diamonds_by_color, mean_price = mean(price))

# 1. make first barchart
b1 = ggplot(aes(clarity, mean_price), data = diamonds_mp_by_clarity) + 
geom_bar(stat = 'identity')

# 2. make second barchart
b2 = ggplot(aes(color, mean_price), data = diamonds_mp_by_color) + 
geom_bar(stat = 'identity')

# 3. examine by cut
diamonds_by_cut = group_by(diamonds, cut)
diamonds_mp_by_cut = summarise(diamonds_by_cut, mean_price = mean(price))

# 4. make third barchart
b3 = ggplot(aes(cut, mean_price), data = diamonds_mp_by_cut) + 
geom_bar(stat = 'identity')

library(gridExtra)
grid.arrange(b1, b2, b3, ncol = 1)
```

# Gapminder Revisted
```{r}
library('xlsx', quietly = TRUE)
library(reshape2)

gapminder_employment_data = read.xlsx('indicator_t above15employ.xlsx', sheetIndex = 1)

summary(gapminder_employment_data)

```

```{r more graphs}

p1 =ggplot(aes(x=gapminder_employment_data$X2005), data = gapminder_employment_data) + geom_histogram()+ xlab('Employment to population %') + ylab('Number of countries') + ggtitle('Year 2005')

p2 = ggplot(aes(x=gapminder_employment_data$X2006), data = gapminder_employment_data) + geom_histogram() + xlab('Employment to population %') + ylab('Number of countries') + ggtitle('Year 2006')

p3 = ggplot(aes(x=gapminder_employment_data$X2007), data = gapminder_employment_data) + geom_histogram() + xlab('Employment to population %') + ylab('Number of countries') + ggtitle('Year 2007')


library(gridExtra)
 grid.arrange(p1, p2, p3, ncol = 3)
```
## Applying a few layers onto the plots
```{r more graphs cont}

p1 =ggplot(aes(x=gapminder_employment_data$X2005), data = gapminder_employment_data) + geom_histogram() + xlab('Employment to population %') + ylab('Number of countries') + ggtitle('Year 2005') + 
  scale_y_log10()

p2 = ggplot(aes(x=gapminder_employment_data$X2006), data = gapminder_employment_data) + geom_histogram() + xlab('Employment to population %') + ylab('Number of countries') + ggtitle('Year 2006')+ 
  scale_y_log10()

p3 = ggplot(aes(x=gapminder_employment_data$X2007), data = gapminder_employment_data) + geom_histogram() + xlab('Employment to population %') + ylab('Number of countries') + ggtitle('Year 2007')+ 
  scale_y_log10()


library(gridExtra)
 grid.arrange(p1, p2, p3, ncol = 3)
```




