---
title: "Explore One Variiable"
author: "Alex Gunagwera"
date: "15 Mart 2018"
output: html_document
---

# Load the Diamonds dataset
```{r}
library(ggplot2) #must load the ggplot package first
data(diamonds) #loads the diamonds data set since it comes with the ggplot package

# lets take a look at its summary
summary(diamonds)
```

## Create a histogram of the price of all  the diamonds
```{r}
hist(x = diamonds$price)
```
#### summary statics for the price distribution
```{r}
summary(diamonds$price)

```
#### Diamonds Cost Analysis
```{r}
lessThan500 = diamonds$price < 500
sum(lessThan500)

lessThan250 = diamonds$price < 250
sum(lessThan250)

greaterThanEqual15000 = diamonds$price >= 15000
sum(greaterThanEqual15000)
```
### Cheaper diamonds
```{r}
# Try limiting the x-axis, altering the bin width,
# and setting different breaks on the x-axis.
qplot(x = price, data = diamonds, binwidth = 10) +
  scale_x_continuous(limits = c(0, 10000),
                     breaks = seq(0, 1000, 50))
```

### Lets Play some more
```{r}
qplot(x = price, data = diamonds, binwidth = 10) +
  scale_x_continuous(xlim() = c(0, 10000),
                     breaks = seq(0, 10000, 1))
```
### Lets get a bit serious now and get some meaningful data
```{r}
ggplot(aes(x = price), data = diamonds) +
  geom_histogram() +
  scale_x_continuous(limits = c(0, 15000))
```

# Let's break the diamonds by cut now
```{r}
# Break out the histogram of diamond prices by cut.

# You should have five histograms in separate
# panels on your resulting plot.

ggplot(aes(x = price), data = diamonds) +
  geom_histogram() +
  scale_x_continuous(limits = c(0, 15000), breaks = seq(0, 50, 2)) +
  facet_wrap(~cut)
```
### More on Facets
```{r}
qplot(x = price, data = diamonds) + facet_wrap(~cut)
```
### Free scaled Facets
```{r}
qplot(x = price, data = diamonds) + facet_wrap(~cut, scales = "free")
```
### Price per carat
```{r}
# Create a histogram of price per carat
# and facet it by cut. You can make adjustments
# to the code from the previous exercise to get
# started.

# Adjust the bin width and transform the scale
# of the x-axis using log10.

qplot(x = price/carat, data = diamonds) +
  facet_wrap(~cut, scales = 'free_y') +
  scale_x_log10()
```

### now lets transform the x-axis using log10
```{r}
# Create a histogram of price per carat
# and facet it by cut. You can make adjustments
# to the code from the previous exercise to get
# started.

# Adjust the bin width and transform the scale
# of the x-axis using log10.
p1 = ggplot(aes(x = price), y=carat, data = diamonds) + geom_histogram(binwidth=0.005) + facet_wrap(~cut)

p2 = p1 + scale_x_log10()
p2
```

## Lets test our skills using box plots with any of the categorical variables
```{r}
## Boxplot on Price and cut:
qplot(x = cut , y = price , data = diamonds,
geom = 'boxplot' , main = 'Boxplot on the price and cut')+
scale_y_continuous(limits = c(0,6000),breaks = seq(0,15000,1000))
```
## A Box plot of color and price using qplot
```{r}
##Boxplot on Price and color:
qplot(x = color , y = price , data = diamonds,
geom = 'boxplot' , main = 'Boxplot on the price and color')+
scale_y_continuous(limits = c(0,6000),breaks = seq(0,6000,1000))
```
## IQRs in r
```{r}
quantile(x = diamonds$price)
```
### Lets play a little more
```{r}
quantile(subset(diamonds, color == "D")$price)
```
### Lets play a little more
```{r}
quantile(subset(diamonds, color == "J")$price)
```
### Lets play a little more
```{r}
IQR(subset(diamonds, color == "D")$price)
```
### Lets play a little more
```{r}
IQR(subset(diamonds, color == "J")$price)
```
# Box Plot - examine price per carat
```{r}
# Investigate the price per carat of diamonds across
# the different colors of diamonds using boxplots.
qplot(x=color,y = price/carat,data = diamonds,
      geom = "boxplot")
```
## Frequency Polygon

```{r}
qplot(data=diamonds, x=carat, xlab='Carat', ylab='Frequency', binwidth=0.1, geom='freqpoly') + scale_x_continuous(breaks=seq(0,5,0.2)) + scale_y_continuous(breaks=seq(0,12000,2000))
```

### Gapminder World Question
```{r}
library('xlsx', quietly = TRUE)
library(reshape2)

gapminder_employment_data = read.xlsx('indicator_t above15employ.xlsx', sheetIndex = 1)

summary(gapminder_employment_data)

```

```{r}
# get rid of NA rows and columns
gapminder_employment_data[ncol(gapminder_employment_data)] <- NULL
gapminder_employment_data <- gapminder_employment_data[!is.na(gapminder_employment_data[[1]]),]
```

## Lets plot some graphs
```{r}
ggplot(aes(x=gapminder_employment_data$X2006), data = gapminder_employment_data) + geom_histogram() + xlab('Total employed') + ylab('Numbe of countries') + ggtitle('Year 2006')
```
