Checking out Pseudo Facebook Data
========================================================

***

### What to Do First?
Notes:

***

### Pseudo-Facebook User Data
Notes:

```{r Pseudo-Facebook User Data}
  setwd("B:/Akad/B5/BigData/udacityCodes/Lesson3")
  list.files()
  pf <- read.csv("pseudo_facebook.tsv", sep = "\t")
  names(pf)
```

***

### Histogram of Users' Birthdays 

```{r Histogram of Users\' Birthdays}
library(ggplot2)
qplot( x = dob_day, data = pf)

```


***
### Faceting

```{r Faceting}
# qplot(x = dob_day, data = pf) + 
#   scale_x_continuous(breaks = 1:31) +
#   facet_wrap(~dob_month, ncol = 3)
ggplot(data = pf, aes(x = dob_day)) +
  geom_histogram(binwidth = 1) +
  scale_x_continuous(breaks = 1:31) +
  facet_wrap(~dob_month)
```

## Getting friend count

```{r Friend Count}
ggplot(aes(x = friend_count), data = pf) +
  geom_histogram()
```



***

### Limiting the Axes
Notes: we may need to limit the bounds of our axes..

```{r Limiting the Axes}
# qplot(x = friend_count, data = pf, xlim = c(0,1000))
# 
# ## alternatively
# qplot(x = friend_count, data = pf) + 
#   scale_x_continuous(limits = c(0, 1000))


ggplot(aes(x = friend_count), data = pf) +
  geom_histogram() +
  scale_x_continuous(limits = c(0, 1000))
```

### Exploring with Bin Width

***

### Adjusting the Bin Width
```{r}
## Original code:

qplot(x = friend_count, data = pf, binwidth = 25) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50))

## Equivalent ggplot syntax:

ggplot(aes(x = friend_count), data = pf) +
  geom_histogram(binwidth = 25) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50))

```

### Faceting Friend Count
```{r Faceting Friend Count}
# What code would you add to create a facet the histogram by gender?
# Add it to the code below.
qplot(x = friend_count, data = pf, binwidth = 10) +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50))

## option one - creating a facet
qplot(x = friend_count, data = pf) +
  facet_grid(gender ~ .)
```
```{r}
## option two, creating a facet -- ggplot
ggplot(aes(x = friend_count), data = pf) +
  geom_histogram() +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50)) +
  facet_wrap(~gender)

```


***

### Omitting NA Values
Notes:

```{r Omitting NA Values}
ggplot(aes(x = friend_count), data = subset(pf, !is.na(gender))) +
  geom_histogram() +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50)) +
  facet_wrap(~gender)
```

***

### Statistics 'by' Gender
Notes: Lets see who's got more friends on average

```{r Statistics \'by\' Gender}
table(pf$gender)
by(pf$friend_count, pf$gender, summary)
```

#### Who on average has more friends: men or women?
Response:

#### What's the difference between the median friend count for women and men?
Response: 22

#### Why would the median be a better measure than the mean?
Response: median is not susceptible to changes such as tailed data 

***

### Tenure
Notes:

```{r Tenure}
ggplot(aes(x = tenure), data = pf) +
  geom_histogram(binwidth = 30, color = 'black', fill = '#099DD9')

```

***

#### How would you create a histogram of tenure by year?

```{r Tenure Histogram by Year}
## For years
ggplot(aes(x = tenure/365), data = pf) +
  geom_histogram(binwidth = .25, color = 'black', fill = '#F79420')
```

***

### Labeling Plots
Notes:

```{r Labeling Plots}
ggplot(aes(x = tenure / 365), data = pf) +
  geom_histogram(color = 'black', fill = '#F79420') +
  scale_x_continuous(breaks = seq(1, 7, 1), limits = c(0, 7)) +
  xlab('Number of years using Facebook') +
  ylab('Number of users in sample')
```

***

### User Ages
Notes:

```{r User Ages}
ggplot(aes(x = age), data = pf) +
  geom_histogram(binwidth = 1, fill = '#5760AB') +
  scale_x_continuous(breaks = seq(0, 113, 5))
```

***

# Transforming Data
```{r}
qplot(x = friend_count, data = pf)

summary(pf$friend_count)

summary(log10(pf$friend_count + 1))

summary(sqrt(pf$friend_count))
# 
# > summary(pf$friend_count)
#    Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
#     0.0    31.0    82.0   196.4   206.0  4923.0 
# > 
# > summary(log10(pf$friend_count + 1))
#    Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
#   0.000   1.505   1.919   1.868   2.316   3.692 
# > 
# > summary(sqrt(pf$friend_count))
#    Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 

```

## Creating multiple plots using grid plot - "using qplot"
```{r}
library('gridExtra')
p1 = qplot(x = friend_count, data = pf)

p2 = qplot(x = log10(pf$friend_count + 1), data = pf)

p3 = qplot(x = sqrt(friend_count), data = pf)

grid.arrange(p1, p3, p2,  ncol= 1)
```
## Creating multiple plots using grid plot - "using ggplot"
```{r}
p1 = ggplot(aes(x = friend_count), data = pf) + geom_histogram()

p2 = p1 + scale_x_log10()

p3 = p1 + scale_x_sqrt()

grid.arrange(p1, p3, p2,  ncol= 1)
```

### Add a Scaling Layer


```{r Add a Scaling Layer}
library(gridExtra)
ggplot(aes(x = friend_count), data = pf) +
  scale_x_log10()
```

***


### Frequency Polygons

```{r Frequency Polygons}
ggplot(aes(x = friend_count, y = ..count../sum(..count..)),
       data = subset(pf, !is.na(gender))) +
  geom_freqpoly(aes(color = gender), binwidth=10) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50)) +
  xlab('Friend Count') +
  ylab('Proportion of users with that friend count')
```

***

### Likes on the Web
Notes:

```{r }
ggplot(aes(x = www_likes), data = subset(pf, !is.na(gender))) +
  geom_freqpoly(aes(color = gender)) +
  scale_x_log10()
```


***
```{r Likes on the Web}
ggplot(aes(x = www_likes), data = subset(pf, !is.na(gender))) +
  geom_freqpoly(aes(color = gender)) +
  scale_x_log10()
```
